---
title: "Homework Day 6"
author: "Barrett Bryson"
date: "1/15/2015"
output: html_document
---

**Problem 4**<br>
**a)** 10% <br>
**b)** 1% <br>
**c)** 10^-98% <br>
**d)** As p get larger the data captured in each range get smaller and smaller. By the time we get to p=7 you need an extremely large data set to have a significant enough number of neighbors to make an accurate prediction. <br>
**e)** p=1 l=.1 <br>
p=2 l=sqrt(.1)=0.3162278<br>
p=100 l=.1^(1/100)=0.9772372<br>
<br>
**Problem 6**<br>
**a)** 
```{r}
exp(-6+.05*(40)+1*(3.5))/(1+exp(-6+.05*(40)+1*(3.5)))
```
<br>
**b)**
```{r}
2.5/.05
```
<br>
**Problem 9**<br>
**a)** 27% <br>
**b)** .19 <br>
<br>
```{r,echo=FALSE}
library("ISLR")
```
**Problem 10** <br>
**a)**
```{r,echo=FALSE}
summary(Weekly)
pairs(Weekly)
cor(Weekly[-9])
```
It appears there is some correlation between volume and year.<br>
**b)**
```{r}
attach(Weekly)
glm.fit = glm(Direction~.-Today,data=Weekly,family=binomial)
summary(glm.fit)
```
lag 2 appears to be the only statiscally significant predictor.<br>
**c)**
```{r}
glm.probs = predict(glm.fit, type = "response")
glm.pred = rep("Down", length(glm.probs))
glm.pred[glm.probs > 0.5] = "Up"
xtabs(~glm.pred+Weekly$Direction)
```
The prediction is right slightly more than half of the time. It predicts the market is going up very frequently. <br>
**d)**
```{r}
train = (Year < 2009)
Weekly.20092010 = Weekly[!train, ]
glm.fit2 = glm(Direction~Lag2,data=Weekly,family=binomial)
summary(glm.fit2)
glm.probs2 = predict(glm.fit2, Weekly.20092010, type = "response")
glm.pred2 = rep("Down", length(glm.probs2))
glm.pred2[glm.probs2 > 0.5] = "Up"
xtabs(~glm.pred2+Weekly.20092010$Direction)
```
it is now correct 62% of the time.<br>
<br>
**Problem 12**<br>
**a)**
```{r}
Power = function(){
  return(2^3)
}
Power()
```
**b)**
```{r}
Power2 = function(x, a){
  return(x^a)
}
Power2(3,8)
```
**c)**
```{r}
Power2(10,3)
Power2(8,17)
Power2(131,3)
```
**d)**
```{r}
Power3 = function(x, a){
  return(x^a)
}
```
**e)**
```{r,echo=FALSE}
plot(c(1:10),Power3(c(1:10),2),xlab="x",ylab="Y=x^2",main="Y as a function of x")
plot(c(1:10),Power3(c(1:10),2),xlab="x",ylab="Y=x^2",log="x",main="Log Scale x")
plot(c(1:10),Power3(c(1:10),2),xlab="x",ylab="Y=x^2",log="y",main="Log Scale Y")
plot(c(1:10),Power3(c(1:10),2),xlab="x",ylab="Y=x^2",log="xy",main="Log Scale x & Y")
```
**f)**
```{r}
PlotPower = function(x,a){
  plot(x,x^a,xlab="x",ylab="Y=x^a",main="Y as a function of x")
}
PlotPower(c(1:10),3)
```