---
title: "Homework 4 W80"
author: "Austin Harnsberger"
date: "1/15/2015"
output: html_document
---
```{r}
library(ISLR)
```  
**4)**  
  **A)** We will use 1/(number of available observations) of the observations to determine our prediction.  
  **B)** We will use 2/(number of available observations) of the observations for our predictions.  
  **C)** We use a very large fraction of the available observatations, 100/(number of available observations) to make our predictions.  
  **D)** As p increases, the number of observations necessary for predictions increases, making the observer have to search further away from the test point to meet the quota of observations. As p increases the model for the KNN becomes more and more linear and rigid.  
**6)**  
  **A)**
  ```{r}
  A = exp(-6+.05*40+3.5)/(1+exp(-6+.05*40+3.5))
  A
  ```  
  **B)** The student would need 50 hours minimum to have a 50% chance of getting an A with a 3.5 GPA.  
**9)**  
  **A)**  The fraction of people who default with odds of .37 is 21%  
  **B)**  The odds of a person defaulting with 16% chance are .23  
**10)**
  **A)** 
  ```{r}
  names(Weekly)
  summary(Weekly)
  ```
  Most of the means and medians are close together between columns and all but two of the 1st Qu. are negative.  
  **B)** 
**12)**  
  **A)**  
  ```{r}
  Power = 2^3
  print(Power)
  ```  
  **B)**  
  ```{r}
  Power2 = function(x,a){
    Power2 = x^a
    print(Power2)
  }  
  ```
  **C)**  
  ```{r}
  Power2(8,17)
  Power2(131,3)
  ```  
  **D)**  
  ```{r}
  Power3 = function(x,a){
    result = x^a
    return(result)
  }
  ```  
  **E)** 
  ```{r}
  Power3 = function(x){
    Power3 = x^2
    plot(Power3)
  }
  ```  
  **F)**
  ```{r}
  Powerplot = function(x,a){
    Powerplot = x^a
    plot(Powerplot)
  }
  Powerplot(1:10,2)
  ```  