---
title: "Homework day 3"
author: "Barrett Bryson"
date: "1/11/2015"
output: html_document
---
```{r}
library(ISLR)
library (MASS)
```
**Problem 7**<br>
**A)**<br>
Point 1: 3 units
Point 2: 2 units
Point 3: 3.16227 units
Point 4: 2.23606 units
Point 5: 1.41421 units
Point 6: 1.73205 units
<br>
**B)**<br>
With K=1 the prediction would be red because the sole nearest point.<br>
<br>
**C)**<br>
With K=3 the prediction would be red beacuse of the three closest points two are red and one is green.
<br>
**D)**<br>
We would expect a smaller k values so that it closer follows the points.

**Problem 9** <br>
**A)** Qualitative:Name, Origin <br>
Quantative: cylinders, displacement,horsepower, weight, acceleration, year <br><br>
**B)**

```{r}

range(Auto$cylinders)
range(Auto$displacement)
range(Auto$horsepower)
range(Auto$weight)
range(Auto$acceleration)
range(Auto$year)
```
<br>
**C)**
```{r}

mean(Auto$cylinders)
sd(Auto$cylinders)
mean(Auto$displacement)
sd(Auto$displacement)
mean(Auto$horsepower)
sd(Auto$horsepower)
mean(Auto$weight)
sd(Auto$weight)
mean(Auto$acceleration)
sd(Auto$acceleration)
mean(Auto$year)
sd(Auto$year)
```
<br>
**D)**
```{r}
ReducedAuto = Auto[-c(10:85),]

range(ReducedAuto$cylinders)
mean(ReducedAuto$cylinders)
sd(ReducedAuto$cylinders)
range(ReducedAuto$displacement)
mean(ReducedAuto$displacement)
sd(ReducedAuto$displacement)
range(ReducedAuto$horsepower)
mean(ReducedAuto$horsepower)
sd(ReducedAuto$horsepower)
range(ReducedAuto$weight)
mean(ReducedAuto$weight)
sd(ReducedAuto$weight)
range(ReducedAuto$acceleration)
mean(ReducedAuto$acceleration)
sd(ReducedAuto$acceleration)
range(ReducedAuto$year)
mean(ReducedAuto$year)
sd(ReducedAuto$year)
```
<br>
**E)**<br>
```{r,echo=F}
plot(Auto$cylinders,Auto$mpg,xlab="Number of Cylinders",ylab="Miles per Gallon",col="red")
```
<br>
Graph shows a general negative trend between the number of cylinders and the miles per gallon of the car. <br>
```{r,echo=F}
plot(Auto$displacement,Auto$mpg,xlab="Length of Displacement",ylab="Miles per Gallon",col="yellow")
```
<br>
Graph shows a general negative trend between the length of displacement and the miles per gallon of the car. <br>

```{r,echo=F}
plot(Auto$horsepower,Auto$mpg,xlab="Horsepower",ylab="Miles per Gallon",col="blue")
```
<br>
Graph shows a general negative trend between the horsepower of the engine and the miles per gallon of the car. <br>

```{r,echo=F}
plot(Auto$weight,Auto$mpg,xlab="Weight of Car",ylab="Miles per Gallon",col="orange")
```
<br>
Graph shows a general negative trend between the weight of the car and the miles per gallon of the car. <br>

```{r,echo=F}
plot(Auto$acceleration,Auto$mpg,xlab="Acceleration",ylab="Miles per Gallon",col="green")
```
<br>
Graph shows a general positive trend between the acceleration and the miles per gallon of the car. <br>

```{r,echo=F}
plot(Auto$origin,Auto$mpg,xlab="Origin",ylab="Miles per Gallon",col="purple")
```
<br>
Graph shows that japaneese cars tend to do the best, European are second best and American tend to be the worst, in terms of mpg. <br>
<br>
**F)**<br>
I would suggest the inclusion of drag. The different body shapes of different models of cars can lead to difference in the friction due to air.
<br><br>

**Problem 10**<br>
**A)**<br> This data set has 14 columns and 506 rows.<br>
Description of Columns:<br>
crim:
per capita crime rate by town.
<br>
zn:
proportion of residential land zoned for lots over 25,000 sq.ft.
<br>
indus:
proportion of non-retail business acres per town.
<br>
chas:
Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).
<br>
nox:
nitrogen oxides concentration (parts per 10 million).
<br>
rm:
average number of rooms per dwelling.
<br>
age:
proportion of owner-occupied units built prior to 1940.
<br>
dis:
weighted mean of distances to five Boston employment centres.
<br>
rad:
index of accessibility to radial highways.
<br>
tax:
full-value property-tax rate per \$10,000.
<br>
ptratio:
pupil-teacher ratio by town.
<br>
black:
1000(Bk - 0.63)^2
where Bk is the proportion of blacks by town.
<br>
lstat:
lower status of the population (percent).
<br>
medv:
median value of owner-occupied homes in \$1000s.
<br>
<br>
**B)**<br>
```{r,echo=FALSE}
pairs(~crim+zn+indus+chas+nox+rm+age+dis+rad+tax+ptratio+black+lstat+medv,Boston)
```
This allows us to quickly spot correlations in the data<br>
