---
title: "homework 4"
author: "Julia Van Dyke"
date: "January 13, 2015"
output: html_document
---

#**1**
```{r}
library(ISLR)
summary(lm(mpg~horsepower,data=Auto))
```
#i. There is a relationship, this is shown by the low p-value
#ii. The relationship is pretty strong
#iii. The relationship is negative, shown by the negative coefficient
#iv
```{r}
39.9359-.1578*(98)
confint(lm(mpg~horsepower,data=Auto))
```
#b
```{r, echo=FALSE}
plot(Auto$horsepower,Auto$mpg)
abline(lm(mpg~horsepower,data=Auto),col="red")
```
#c
```{r}
plot(lm(mpg~horsepower,data=Auto))
```
#looking at the first graph, we see more residuals above the line than below.
#**10**
#a
```{r}
lm.carseats <- lm(Sales~Price+Urban+US,data=Carseats)
summary(lm.carseats)
```
#If urban and US are both constant, then for every dollar increase in price, the total sales will drop by about $54. If the seat is sold in the US, it is expected to generate an extra $1200.
#c
#X1=price in dollars
#X2=1 if urban, 0 if not urban
#X3=1 if US, 0 if not US
#Y=Sales in thousands of dollars
#Y=13.043469-0.054459(X1)-0.021916(X2)+1.200573(X3)
#d
#Urban
#e

#**1**
```{r}
library(ISLR)
summary(lm(mpg~horsepower,data=Auto))
```
#i. There is a relationship, this is shown by the low p-value
#ii. The relationship is pretty strong
#iii. The relationship is negative, shown by the negative coefficient
#iv
```{r}
39.9359-.1578*(98)
confint(lm(mpg~horsepower,data=Auto))
```
#b
```{r, echo=FALSE}
plot(Auto$horsepower,Auto$mpg)
abline(lm(mpg~horsepower,data=Auto),col="red")
```
#c
```{r}
plot(lm(mpg~horsepower,data=Auto))
```
#looking at the first graph, we see more residuals above the line than below.
#**10**
#a
```{r}
lm.carseats <- lm(Sales~Price+Urban+US,data=Carseats)
summary(lm.carseats)
```
#If urban and US are both constant, then for every dollar increase in price, the total sales will drop by about $54. If the seat is sold in the US, it is expected to generate an extra $1200.
#c
#X1=price in dollars
#X2=1 if urban, 0 if not urban
#X3=1 if US, 0 if not US
#Y=Sales in thousands of dollars
#Y=13.043469-0.054459(X1)-0.021916(X2)+1.200573(X3)
#d
#Urban
#e
```{r}
lm.carseats2 <- lm(Sales~Price+US,data=Carseats)
```
#f
#The second one fits better, it has a better value for R^2 and a lower p-value.
#g
```{r}
confint(lm.carseats2)
```
#h
```{r}
plot(lm.carseats2)
```
#The residuals seem to be equally distributed above and below the line
#**14**
#a
```{r}
set.seed(1)
x1=runif(100)
x2=0.5*x1+rnorm(100)/10
y=2+2*x1+0.3*x2+rnorm(100)
```
#y=2+2*x1+0.3*x2+rnorm(100)
#b
```{r}
cor(x1,x2)
plot(x1,x2)
```
#c
```{r}
lm.14 <- lm(y~x1+x2)
summary(lm.14)
```
#Y=1.4396(x1)+1.0097(x2)
#We reject the null hypothesis for x1, but not x2. 
#d
```{r}
lm.14.1 <-lm(y~x1)
summary(lm.14.1)
```
#e
```{r}
lm.14.2 <- lm(y~x2)
summary(lm.14.2)
```
#f
#yes. When the model uses both x1 and x2, the p-values are fairly large, but when x1 and x2 are used seperately they're very small.
#g
```{r}
x1=c(x1, 0.1)
x2=c(x2, 0.8)
y=c(y,6)
lm.14 <- lm(y~x1+x2)
summary(lm.14)
lm.14.1 <-lm(y~x1)
summary(lm.14.1)
lm.14.2 <- lm(y~x2)
summary(lm.14.2)
```
#The added point is both an outlier and a high leverage point.
#The coefficients are significantly different.
